\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}
\usepackage{etaremune}

\def\name{Jon Green}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {political science, political methodology, text as data, networks, causal inference, public opinion, political behavior, American politics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \href{https://www.lazerlab.net/}{Network Science Institute} \\
    Northeastern University \\
    177 Huntington Avenue \\
  Boston, MA, 02115
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Email: & jo.green@northeastern.edu \\
    Phone: & (434) 806-3531 \\
    Website: & jgreen4919.github.io \\
  \end{tabular}
\end{minipage}

\section*{Education}

\begin{itemize}
    \item Ph.D., Political Science, Ohio State University (2016-2020)
	\item B.A. with High Honors in Political Science, Kenyon College (2009-2014)
\end{itemize}

\section*{Academic Appointments and Affiliations}

\begin{itemize}

\item Network Science Institute, Northeastern University (2020-present)\\
- Senior Research Scientist (2021-present)\\
- Affiliated Researcher, NULab for Text, Maps, and Networks (2022-present) \\
- Part-Time Lecturer (January-May 2022)\\
- Postdoctoral Fellow (2020-2021)

\item Shorenstein Center on Media, Politics and Public Policy, Harvard Kennedy School (2021-present)\\
- Fellow (2021-present)
\end{itemize}

\section*{Publications}

\subsection*{Books}
\begin{etaremune}
\item  \textbf{Green, Jon}, and Mark H. White II. \textit{Machine Learning for Experiments in the Social Sciences.}  Conditionally accepted, Cambridge University Press, Elements Series in Experimental Political Science.
\end{etaremune}

\subsection*{Peer Reviewed Journal Articles}

\subsubsection*{Political Science}

\begin{etaremune}

\item Robertson, Ronald E., \textbf{Jon Green}, Damian Ruck, Katherine Ognyanova, Christo Wilson, and David Lazer.  "Engagement Outweighs Exposure to Partisan and Unreliable News within Google Search." Conditionally accepted, \textit{Nature}.\\
Preprint: \url{https://arxiv.org/abs/2201.00074}

\item \textbf{Green, Jon}, James N. Druckman, Matthew A. Baum, David Lazer, Katherine Ognyanova, and Roy H. Perlis. "Depressive Symptoms and Conspiracy Beliefs." Accepted, \textit{Applied Cognitive Psychology}. \\
Preprint: \url{https://www.ipr.northwestern.edu/documents/working-papers/2022/wp-22-22.pdf}

\item Chewning, Taylor K., \textbf{Jon Green}, Hans J.G. Hassell, and Matthew R. Miles. "Campaign Principal-Agent Problems: Volunteers as Faithful and Representative Agents." Accepted, \textit{Political Behavior}

\item Lacombe, Matthew, Matthew D. Simonson, \textbf{Jon Green}, and James N. Druckman. "Social Disruption, Gun Buying, and Anti-System Beliefs." Accepted, \textit{Perspectives on Politics}. \\
Preprint: \url{https://www.ipr.northwestern.edu/documents/working-papers/2022/wp-22-13.pdf}

\item \textbf{Green, Jon}, Brian Schaffner, and Sam Luks. "Strategic Discrimination in the 2020 Democratic Primary."  Accepted, \textit{Public Opinion Quarterly}.\\
Preprint: \url{https://osf.io/25kew/}

\item  \textbf{Green, Jon}, James N. Druckman, Matthew A. Baum, David Lazer, Katherine Ognyanova, Matthew Simonson, Jennifer Lin, Mauricio Santillana, and Roy Perlis. In press. "Using General Messages to Persuade on a Politicized Scientific Issue." \textit{British Journal of Political Science}. \\
Preprint:  \url{https://osf.io/7tn4d/}

\item  \textbf{Green, Jon}, William Hobbs, Stefan McCabe, and David Lazer. 2022. "Online Engagement with 2020 Election Misinformation and Turnout in the 2021 Georgia Runoff Election"  \textit{Proceedings of the National Academy of Sciences}  119(34): e2115900119. \\
DOI: 10.1073/pnas.2115900119

\item \textbf{Green, Jon}. 2021. "Does Race Stop at the Water's Edge? Elites, the Public, and Support for Foreign Intervention among White U.S. Citizens over Time." \textit{Political Science Quarterly} 136(2): 339-361. \\
DOI: 10.1002/polq.13168

\item Conroy, Meredith, and \textbf{Jon Green}. 2020. "It Takes a Motive: Communal and Agentic Articulated Interest and Candidate Emergence."  \textit{Political Research Quarterly} 73(4): 942-956. \\
DOI: 10.1177/1065912920933668

\item \textbf{Green, Jon}, Jared Edgerton, Daniel Naftel, Kelsey Shoub, and Skyler Cranmer. 2020. "Elusive Consensus: Polarization in Elite Communication on the COVID-19 Pandemic." \textit{Science Advances} 6(28): eabc2717. \\
DOI: 10.1126/sciadv.abc2717

\item \textbf{Green, Jon}. 2019. "Floating Policy Voters in the 2016 U.S. Presidential Election." \textit{Electoral Studies} 67. \\
DOI: 10.1016/j.electstud.2019.03.004

\item \textbf{Green, Jon}, and Sean McElwee. 2019. "The Differential Effects of Economic Conditions and Racial Attitudes in the Election of Donald Trump." \textit{Perspectives on Politics} 17(2): 358-379. \\
DOI: 10.1017/S1537592718003365

\item Neblo, Michael, William Minozzi, Kevin M. Esterling, \textbf{Jon Green}, Jonathon Kingzette, and David M. J. Lazer. 2016. "The need for a translational science of democracy." \textit{Science} 355(6328), 914-915.\\
DOI: 10.1126/science.aal3900

\end{etaremune}

\subsubsection*{Other Social Science}

\begin{etaremune}

\item Perlis Roy H., Mauricio Santillana, Katherine Ognyanova, Alauna Safarpour, Kristin Lunz Trujillo, Matthew D. Simonson, \textbf{Jon Green}, Alexi Quintana, and James N. Druckman. In press. "Prevalence and correlates of long COVID symptoms among U.S. adults." \textit{JAMA Network Open}.

\item Klein, Brennan, Nicholas Generous, Matteo Chinazzi, Zarana Bhadricha, Rishab Gunashekar, Preeti Kori, Bodian Li, Stefan McCabe, \textbf{Jon Green}, David Lazer, Christopher R. Marsicano, Samuel V. Scarpino, and Alessandro Vespignani. "Higher education responses to COVID-19 in the United States: Evidence for the impacts of university policy." \textit{PLOS Digital Health} 1(6): e0000065. \\
DOI: 10.1371/journal.pdig.0000065

\item  Perlis, Roy H., Matthew D. Simonson, \textbf{Jon Green}, Jennifer Lin, Alauna Safarpour, Kristin Lunz Trujillo, Alexi Quintana, Hanyu Chwe, John Della Volpe, Katherine Ognyanova, Mauricio Santillana,  James Druckman, David Lazer, and Matthew A. Baum. 2022. "Prevalence of Firearm Ownership Among Individuals With Major Depressive Symptoms." \textit{JAMA Network Open} 5(3): e223245. \\
DOI: 10.1001/jamanetworkopen.2022.3245

\item  Perlis, Roy H., Katherine Ognyanova, Mauricio Santillana, Jennifer Lin, James Druckman, David Lazer,  \textbf{Jon Green}, Matthew D. Simsonson, Matthew A. Baum, and John Della Volpe. 2022. "Association of Major Depressive Symptoms With Endorsement of COVID-19 Vaccine Misinformation Among US Adults." \textit{JAMA Network Open} 5(1): e2145697. \\
DOI: 10.1001/jamanetworkopen.2021.45697

\item  Perlis, Roy H., \textbf{Jon Green}, Matthew D. Simonson, Katherine Ognyanova, Mauricio Santillana, Jennifer Lin, Alexi Quintana, Hanyu Chwe, James Druckman, David Lazer, Matthew A. Baum, and John Della Volpe. 2021. "Association Between Social Media Use and Self-reported Symptoms of Depression in US Adults." \textit{JAMA Network Open} 4(11): e2136113. \\
DOI: 10.1001/jamanetworkopen.2021.36113

\item  Perlis, Roy H., Katherine Ognyanova, Alexi Quintana, \textbf{Jon Green}, Mauricio Santillana, Jennifer Lin, James Druckman, David Lazer, Matthew D. Simonson, Matthew A. Baum, and Hanyu Chwe. 2021. "Gender-specificity of resilience in major depressive disorder." \textit{Depression \& Anxiety} 38(10): 1026-1033. \\
DOI: 10.1002/da.23203

\item  Perlis, Roy H., Mauricio Santillana, Katherine Ognyanova, \textbf{Jon Green}, James Druckman, David Lazer, and Matthew A. Baum. 2021. "Factors Associated With Self-reported Symptoms of Depression Among Adults With and Without a Previous COVID-19 Diagnosis." \textit{JAMA Network Open} 4(6): e2116612. \\
DOI: 10.1001/jamanetworkopen.2021.16612
\end{etaremune}

\subsection*{Peer Reviewed Conference Proceedings}

\begin{etaremune}
\item Horne, Benjamin D. Maur\'{i}cio Gruppi, Kenneth Joseph, \textbf{Jon Green}, John P. Wihbey, and Sibel Adali. 2022. "NELA-Local: A Dataset of U.S. Local News Articles for the Study of County-Level News Ecosystems." Proceedings of the International AAAI Conference on Web and Social Media 16(1), 1275-1284\\
Dataset URL: https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/GFE66K

\item Joseph, Kenneth, Benjamin D. Horne, \textbf{Jon Green}, and John P. Wihbey. 2022. "Local News and COVID in the U.S.: Relationships between Coverage, Cases, Deaths, and Audience." Proceedings of the International AAAI Conference on Web and Social Media, 16(1), 441-452.\\
DOI: 10.48550/arXiv.2111.08515

\item Joseph, Kenneth, Sarah Shugars, Ryan Gallagher, \textbf{Jon Green}, Alexi Quintana Mathé, Zijian An and David Lazer. 2021. "(Mis)alignment Between Stance Expressed in Social Media Data and Public Opinion Surveys." Proceedings of the 2021 Conference on Empirical Methods in Natural Language Processing, pages 312-324. \\
DOI: 10.18653/v1/2021.emnlp-main.27
\end{etaremune}

\subsection*{Book Chapters}

\begin{etaremune}
\item \textbf{Green, Jon}, Jonathon Kingzette, and Michael Neblo. 2019. "Deliberative Democracy and Political Decision Making" in \textit{The Oxford Research Encyclopedia of Politics}, eds. David Redlawsk and Cengiz Erisen.\\
DOI: 10.1093/acrefore/9780190228637.013.917
\end{etaremune}

\section*{Preprints and Manuscripts Under Review}

\subsection*{Revise and Resubmit}

\begin{itemize}

\item \textbf{Green, Jon}, Meredith Conroy, and Ciera Hammond. "Something to Run For: Articulated Interest and Candidate Emergence."  Revise and resubmit, \textit{Political Behavior}.
\begin{itemize}
\item \textit{Presented at the 2019 meeting of the Midwest Political Science Association}
\item Preprint: \url{https://osf.io/5cdp7/}
\end{itemize}

\end{itemize}

\subsection*{Under Review}

\begin{itemize}
\item \textbf{Green, Jon}. "Ideological Structures Among U.S. Political Pundits." %\textit{Under review}.
\begin{itemize}
\item \textit{Presented at the 2021 meetings of the Southern, Western, and Midwest Political Science Associations and the 2022 meeting of the American Political Science Association}
\item Preprint: \url{https://osf.io/2cjse/}
\end{itemize}

\item \textbf{Green, Jon}, James N. Druckman, Matthew A. Baum, Katherine Ognyanova, Matthew D. Simonson, Roy H. Perlis, and David Lazer. "Association Between Facebook Use for COVID-19 Information and Vaccine Skepticism in the United States." %\textit{Under review}.

\item Naftel, Daniel, \textbf{Jon Green}, Kelsey Shoub, Jared Edgerton, Mallory Wagner, and Skyler Cranmer. "Meet the Press: Gendered Conversational Norms in Televised Political Discussions." %\textit{Under review}.
\begin{itemize}
\item Preprint: \url{https://osf.io/my8us/}
\end{itemize}

\item Simonson, Matthew D, Matthew Lacombe, \textbf{Jon Green}, and James N. Druckman. "Guns and Democracy: Anti-System Attitudes, Protest, and Support for Violence Among Pandemic Gun-Buyers."% \textit{Under review}.
\begin{itemize}
\item Preprint: \url{https://www.ipr.northwestern.edu/documents/working-papers/2022/wp-22-37.pdf}
\end{itemize}

\item McCabe, Stefan, \textbf{Jon Green}, Pranav Goel, and David Lazer. "Inequalities in Online Representation: Who follows their own Member of Congress on Twitter?"
\begin{itemize}
\item \textit{Presented at the 2021 meeting of the Political Networks Conference}
\item Preprint: \url{https://osf.io/x4d6n}
\end{itemize} 

\item Benegal, Salil, and \textbf{Jon Green}. "Cost Sensitivity, Partisan Cues, and Support for the Green New Deal." %\textit{Under review}.

%\item Esterling, Kevin, Stefan McCabe, Diogo Ferrari, \textbf{Jon Green}, and David Lazer. "Deplatforming Right-Wing Extremists on Twitter Following the January 6 Insurrection." 
\end{itemize}

\subsection*{Publicly Available Working Papers}

\begin{itemize}
\item \textbf{Green, Jon}, Stefan McCabe, Sarah Shugars, John Harrington, Hanyu Chwe, Luke Horgan, Shuyang Cao, and David Lazer.  "Curation Bubbles: Domain versus URL-level analyses of Partisan Differences in News Sharing on Social Media."
\begin{itemize}
\item \textit{Presented at the 2021 meetings of the Midwest and American Political Science Associations}.
\item Preprint: \url{https://osf.io/vbwer/}
\end{itemize} 

\item  \textbf{Green, Jon}, Matthew A. Baum, James N. Druckman, David Lazer, Katherine Ognyanova, Matthew Simonson, Roy Perlis, and Mauricio Santillana. "Identifying and Measuring Conditional Policy Preferences: The Case of Opening Schools During a Pandemic." 
\begin{itemize}
\item Preprint: \url{https://osf.io/zsh8u/}
\end{itemize}

\item \textbf{Green, Jon}, Jon Kingzette, William Minozzi, and Michael Neblo. "A Speech Act Perspective on the Survey Response." 
\begin{itemize}
\item Preprint: \url{https://osf.io/54ysv/}
\end{itemize}

\item \textbf{Green, Jon}, and Seth Masket. "The Contest After the Contest: Post-Election Narrative Development on Twitter." 
\begin{itemize}
\item \textit{Presented at the American Elections Symposium 2020: Politics in a Time of Crisis (St. Anselm College, 2021) and the 2021 meeting of the Midwest Political Science Association}
\item Preprint: \url{https://www.dropbox.com/s/xv3m14dcfy3pyde/green_masket_MPSA.pdf?dl=0}
\end{itemize}

\item \textbf{Green, Jon}, and Michael Neblo. "Dilemmas of a (Hyper)Extended Republic: Four Levels of Representation in Redistricting." 
\begin{itemize}
\item Preprint: \url{https://osf.io/6k7wa/}
\end{itemize}

\end{itemize}

\section*{Selected Projects in Progress}

\begin{itemize}

\item \textit{Democracy for Good Reasons}, book project with Michael Neblo and William Minozzi.

\item "How Do Ideological Coalitions Learn? Structures of Influence Among U.S. Political Pundits" with Allison Wan.

\item "Belief Systems as Directed Networks of Attitudes" with Sarah Shugars, Nic Fishman, Samantha Cadenasso, and Peter Levine.
\begin{itemize}
\item \textit{Presented at the 2022 meetings of the American and Midwest Political Science Associations}.
\end{itemize} 

\item "Attitudes in Top-of-the-Head Open-Ended Survey Responses and Social Media Posts" with Will Hobbs.

\item "Divisive or Descriptive?: How Americans Understand Critical Race Theory" with Alauna Safarpour, Kristin Lunz Trujillo, Caroline Pippert, Jennifer Lin, and James N. Druckman.

\item "Covid-19 Spillover Effects onto General Vaccine Attitudes" with Kristin Lunz Trujillo, Alauna Safarpour, David Lazer,  Jennifer Lin, and Matthew Motta. 

\item "Cross-Platform Partisan Posturing in Congressional Speech" with Kelsey Shoub, Lindsey Cormack, and Rachel Blum.

\item "The Partisanship of Problem Definition" with Kelsey Shoub, Cara Nix, Jared Edgerson, Mallory Wagner, Daniel Naftel, and Skyler Cranmer.

\item "New tweetScores" with Stefan McCabe, Allison Wan, and David Lazer.

\end{itemize}

\section*{Reports}

\begin{itemize}

\item  Lazer, David, \textbf{Jon Green},  Katherine Ognyanova, Matthew A. Baum, Jennifer Lin, James N. Druckman, Roy H. Perlis, Mauricio Santillana, and Ata Uslu. July 2021. "Report \#57: Social Media News Consumption and COVID-19 Vaccination Rates." The COVID-19 Consortium for Understanding the Public’s Policy Preferences Across States.

\item  \textbf{Green, Jon}, David Lazer, Matthew A. Baum, Katherine Ognyanova, Roy H. Perlis, James N. Druckman, Adina Gitomer, Matthew D. Simonson, Mauricio Santillana, Jennifer Lin, Ata Uslu, and Alexi Quintana. January 2021. "Report \#50: Update on the Johnson \& Johnson vaccine pause." The COVID-19 Consortium for Understanding the Public’s Policy Preferences Across States.

\item David Lazer, Katherine Ognyanova, \textbf{Jon Green}, Matthew A. Baum, Roy H. Perlis, James N. Druckman, Adina Gitomer, Matthew D. Simonson, Mauricio Santillana, Jennifer Lin, Ata Uslu, and Alexi Quintana. October 2020. "Report \#48: Assessing the impact of the pause in Johnson \& Johnson vaccine use on COVID-19 vaccination intent." The COVID-19 Consortium for Understanding the Public’s Policy Preferences Across States.

\item  \textbf{Green, Jon}, David Lazer, Matthew A. Baum, James N. Druckman, Ata Uslu, Matthew D. Simonson, Katherine Ognyanova, Adina Gitomer, Jennifer Lin, Roy H. Perlis, Mauricio Santillana, and Alexi Quintana. January 2021. "Report \#36: Evaluation of COVID-19 vaccine communication strategies." The COVID-19 Consortium for Understanding the Public’s Policy Preferences Across States.

\item  \textbf{Green, Jon}, David Lazer, Katherine Ognyanova, Matthew A. Baum, James N. Druckman, Adina Gitomer, Matthew D. Simonson, Jennifer Lin, Roy H. Perlis, Mauricio Santillana, Alexi Quintana, and Ata Uslu. January 2021. "Report \#35: Public attitudes towards COVID-19 vaccines." The COVID-19 Consortium for Understanding the Public’s Policy Preferences Across States.

\item Perlis, Roy H., \textbf{Jon Green}, Alexi Quintana, Adina Gitomer, Hanyu Chwe, Matthew Simonson, David Lazer, Matthew A. Baum, Jennifer Lin, Katherine Ognyanova, James N. Druckman, and Mauricio Santillana. October 2020. "Report \#23: Depression Among Young Adults." The COVID-19 Consortium for Understanding the Public’s Policy Preferences Across States.

\item Lazer, David, Alexi Quintana, \textbf{Jon Green}, Katherine Ognyanova, Hanyu Chwe, Roy H. Perlis, Matthew A. Baum, Adina Gitomer, James N. Druckman, Mauricio Santillana, Jennifer Lin, and Matthew Simonson. 2020. "Report \#20: Public Opinion Around Federal and State Reactions to COVID-19." The COVID-19 Consortium for Understanding the Public’s Policy Preferences Across States.

\item \textbf{Green, Jon}, David Lazer, Matthew A. Baum, Adina Gitomer, Alexi Quintana, Katherine Ognyanova, James N. Druckman, Roy H. Perlis, Mauricio Santillana, Hanyu Chwe, Jennifer Lin, and Matthew Simonson. October 2020. "Report \#19: Pandemic-Related Factors Associated with Candidate Preferences." The COVID-19 Consortium for Understanding the Public’s Policy Preferences Across States.

\item Lazer, David, \textbf{Jon Green}, Matthew A. Baum, Alexi Quintana, Katherine Ognyanova, Adina Gitomer, James N. Druckman, Matthew Simonson, Hanyu Chwe, Roy H. Perlis, Jennifer Lin, and Mauricio Santillana. October 2020. "Report \#16: Partisan Differences in Intention to Vote by Mail." The COVID-19 Consortium for Understanding the Public’s Policy Preferences Across States.

\item Baum, Matthew A., Roy H. Perlis, Katherine Ognyanova, Hanyu Chwe, David Lazer, James N. Druckman, \textbf{Jon Green}, Mauricio Santillana, John Della Volpe, Alexi Quintana, and Matthew Simonson. August 2020. "Report \#11: Perceptions of School Reopening Safety in the United States." The COVID-19 Consortium for Understanding the Public’s Policy Preferences Across States.

\item \textbf{Green, Jon}, Emily Ann Israelson, Abigail Kielty, Jonathon Kingzette, and Michael Neblo. 2019. "Civility in the 2018 Ohio Midterm Elections." in Robert G. Boatright ed. 2020 \textit{Civility in the U.S. Senate Debates}. Tucson, AZ: National Institute for Civil Discourse.

\item Conroy, Meredith, and \textbf{Jon Green}. 2018. "Something to Run For: Candidate Emergence in the Progressive Movement." \textit{Report prepared for Data for Progress and Run for Something.}

\item Acree, Brice, \textbf{Jon Green}, William Minozzi, and Michael Neblo. 2018. "Large Scale Analysis of Topics in Common Ground for Action Forums." \textit{Report prepared for the Kettering Foundation}.

\item Kingzette, Jonathon, and \textbf{Jon Green}. 2018. "Finding Common Ground on Immigration Policy: College Students Want to Welcome Immigrants." \textit{Report prepared for the Kettering Foundation}.
\end{itemize}

\section*{Honors, Awards, and Grants}

\begin{itemize}

\item NetSeed Pilot Grant, Network Science Institute at Northeastern University, 2021, with Sarah Shugars and Peter Levine

\item Student Research Grant, Mershon Center at the Ohio State University, 2020, with Jared Edgerton and Daniel Naftel

\item Francis R. Aumann Award for Best Pre-Conference Presentation, Ohio State University Department of Political Science, 2019

\item William J. Bryan Award for Best Paper in American Politics, Ohio State University Department of Political Science, 2018

\item Joint Learning Agreement with the Kettering Foundation, 2018

\item Perry Scholarship, Ohio State University Department of Political Science, 2018

\item William J. Bryan Award for Best Paper in American Politics, Ohio State University Department of Political Science, 2017

\item Ripley Graduate Research Award, Department of Political Science, Ohio State University, 2017

\item Social and Behavioral Sciences Fellowship, Ohio State University

\item Distinguished University Fellowship, Ohio State University

\item University Fellowship, Ohio State University
\end{itemize}

\section*{Conference Participation}

\subsection*{Presentations}
\begin{itemize}

\item American Political Science Association (2021, 2022)

\item Midwest Political Science Association (2018, 2019, 2021, 2022)

\item Politics and Computational Social Science (2021)

\item Political Networks (2021)

\item Western Political Science Association (2021)

\item American Elections Symposium 2020: Politics in a Time of Crisis, St. Anselm College (2021)

\item Southern Political Science Association (2021)

\item Strategic Partnership for Applied Redistricting Knowledge (2019)

\item Ohio State Graduate Immersion Conference (2019)
\end{itemize}

\subsection*{Service}
\begin{itemize}

\item Panel Discussant, Midwest Political Science Association (2021, 2022)

\item Panel Discussant, American Political Science Association (2021)

\item Panel Chair, Midwest Political Science Association (2021)

\item Paper Discussant, Junior Americanist Workshop Series (2021)

\item Panel Discussant, Southern Political Science Association (2021)

\item Paper Discussant, American Elections Symposium 2020: Politics in a Time of Crisis, St. Anselm College (2021)

\end{itemize}

\section*{Invited Talks}
\begin{itemize}

\item Applications in Text-as-Data. Inter-university Consortium for Political and Social Research (ICPSR), August 8, 2022. 

\item Vaccine Misinformation: A New Report from the COVID States Project, with Matthew A. Baum, David Lazer, Katherine Ognyanova, Mauricio Santillana, and Roy H. Perlis. Shorenstein Center on Media, Politics and Public Policy, Harvard Kennedy School, August 12, 2021.

\item Data for Progress: Using Social Science to Inform Advocacy and Activism. Northeastern University, November 17, 2020. 

\item America Voted. What's Next? With John Elliott, Densil Porteous, and Sarah Longwell. Kenyon College, November 10, 2020. 

\item COVID-19 and Election 2020: Change and Stability in U.S. Electoral Politics, with Tom Wood, Abigail Kielty, Sean Trende, and Kaitlin McClamrock. Ohio State University, May 13, 2020. 
\end{itemize}

\section*{Scholarly Public Engagement}

\begin{itemize}

\item David Lazer, \textbf{Jon Green}, Katherine Ognyanova, Matthew A. Baum, Jennifer Lin, James N. Druckman, Roy Perlis, Mauricio Santillana, Matthew Simonson, and Ata Uslu. "People are more anti-vaccine if they get their covid news from Facebook rather than from Fox News, data shows" The Washington Post's Monkey Cage Blog, July 27, 2021. \\ 
URL: https://www.washingtonpost.com/politics/2021/07/27/people-are-more-anti-vaccine-if-they-get-their-covid-19-news-facebook-rather-than-fox-news-new-data-shows/

\item David Lazer, \textbf{Jon Green}, Matthew A. Baum, Alexi Quintana Mathé, Katherine Ognyanova, Adina Gitomer, James N. Druckman, Matthew Simonson, Hanyu Chwe, Roy H. Perlis, Jennifer Lin, and Mauricio Santillana. "These nine swing states will see the biggest 'blue shift' as ballots are counted after the election" The Washington Post's Monkey Cage Blog, October 21, 2020. \\ 
URL: https://www.washingtonpost.com/politics/2020/10/20/these-9-swing-states-will-see-biggest-blue-shift-ballots-are-counted-after-election/

\item Schaffner, Brian and \textbf{Jon Green}. "Sexism is Probably One Reason Why Elizabeth Warren Didn't Do Better" Data for Progress, March 5, 2020. \\
URL: https://www.dataforprogress.org/blog/3/5/sexism-one-reason-why-warren-didnt-do-better

\item \textbf{Green, Jon}. "What Can We Learn From Asking People to Talk About Candidates?" Data for Progress, February 4, 2020. \\
URL: https://www.dataforprogress.org/blog/2020/2/4/what-can-we-learn-from-asking-people-to-talk-about-candidates

\item Schaffner, Brian and \textbf{Jon Green}. "What Attributes do Democratic Primary Voters Value?" Data for Progress, July 11, 2019. \\
URL: https://www.dataforprogress.org/blog/2019/7/11/what-attributes-do-democratic-primary-voters-value

\item \textbf{Green, Jon}. "The Ideology of Trump's Judges." Memo prepared for Data for Progress and Demand Justice, May 10, 2019. \\
URL: https://www.dataforprogress.org/memos/the-ideology-of-trumps-judges-demand-justice

\item Davis, Nick, and \textbf{Jon Green}. "Sorting All the Way Down." Data for Progress, December 17, 2018. \\
URL: https://wthh.dataforprogress.org/blog/2018/12/17/sorting-all-the-way-down

\item \textbf{Green, Jon}, Sean McElwee, Meredith Conroy, and Colin McAuliffe. "(Not) Fake News? Navigating Competing Claims Regarding Status Threat and Support for Donald Trump." The New West: Official Blog of the Western Political Science Association, May 31, 2018. \\
URL: https://thewpsa.wordpress.com/2018/05/31/not-fake-news-navigating-competing-claims-regarding-status-threat-and-trump-support/

\item McElwee, Sean, and \textbf{Jon Green}. "It sure looks as if Kirsten Gillibrand is running for president." The Washington Post's Monkey Cage Blog, January 1, 2018. \\ 
URL: https://www.washingtonpost.com/news/monkey-cage/wp/2018/01/01/it-sure-looks-as-if-kirsten-gillibrand-is-running-for-president/
\end{itemize}

\section*{Teaching}

\subsection*{Instructor of Record}

\begin{itemize}
\item POLS 5660: The Pandemic and the People: Lessons for American Democracy
\begin{itemize}
\item Northeastern University, Spring 2022
\end{itemize}
\end{itemize}

\subsection*{Teaching Assistant}

\begin{itemize}
\item PSCI 3115: Introduction to the Public Policy Process
\begin{itemize}
\item Ohio State University, Fall 2017
\end{itemize}
\item PSCI 7553: Quantitative Political Analysis III
\begin{itemize}
\item Ohio State University, Fall 2019
\end{itemize}
\end{itemize}

\section*{Research Assistance}
\begin{itemize}
\item  Michael Neblo (Spring 2018 - Summer 2019, Spring 2020)
\end{itemize}

\section*{Service}

\begin{itemize}
\item Reviewer, \textit{American Political Science Review; Journal of Politics; Political Behavior; Political Communication; Political Research Quarterly; Politics, Groups, \& Identities; Politics \& Gender; Proceedings of the National Academy of Sciences; Social Currents; Applied Network Science; New Media and Society; International Journal of Communication; Journal of Information Technology \& Politics; Journal of Computational Social Science; Harvard Kennedy School Misinformation Review; Australian Journal of Political Science; Health Education Research; PLOS One; JAMA Network Open; Oxford University Press; Time-Sharing Experiments for the Social Sciences (TESS)}
\begin{itemize}
Outstanding Reviewer, 2020, \textit{Political Research Quarterly}
\end{itemize}
\item Co-founder, Ohio State Politics and Social Media Working Group
\item Co-founder, Data for Progress
\end{itemize}

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today
      \end{footnotesize}
\end{center}

\end{document}