\documentclass{article}

\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}
\usepackage{etaremune}

\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{amsmath}
\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Jon Green} \\
\normalsize Department of Political Science, Duke University\\
\normalsize jon.green@duke.edu $\mid$ jgreen4919.github.io $\mid$ (434) 806-3531
\end{center}

\noindent \textbf{\underline{Community and Public Engagement}}
	\begin{itemize}
\item How to Think About (and Study) Political Podcasts. Media Effects Empirical Workshop, Columbia University, May 2026 (scheduled).

\item How to Think About (and Study) Political Podcasts. American Politics and Methods Colloquium, University of Minnesota, October 2025.

\item Structure in Ideological Coalitions. Kellogg Center for Science of Science \& Innovation, Northwestern University. February 24, 2025.

\item Election Debrief. Nicholas School of the Environment, Duke University. November 6, 2024.

\item Generative AI in Political Science: Promise and Challenges in Research and Pedagogy. University of Florida, February 28, 2024.

\item U.S. Politics 101. Nicholas School of the Environment, Duke University. February 13, 2024.

\item Presidential Primaries: Public Opinion \& Strategic Voting. The New York Chapter of the American Association for Public Opinion Research. September 20, 2023 (Remote).

\item More than a Game: Political Pundits and the Maintenance of Ideological Coalitions. American Politics Research Group, University of North Carolina - Chapel Hill. September 15, 2023.

\item Applications in Text-as-Data. Inter-university Consortium for Political and Social Research (ICPSR), August 8, 2022 (Remote). 

\item America Voted. What's Next? With John Elliott, Densil Porteous, and Sarah Longwell. Kenyon College, November 10, 2020 (Remote). 

\item COVID-19 and Election 2020: Change and Stability in U.S. Electoral Politics, with Tom Wood, Abigail Kielty, Sean Trende, and Kaitlin McClamrock. Ohio State University, May 13, 2020 (Remote).

\end{itemize}


\end{document}
