\documentclass{article}

\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{amsmath}
\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Jon Green} \\
\normalsize Department of Political Science, Duke University\\
\normalsize jon.green@duke.edu $\mid$ jgreen4919.github.io $\mid$ (434) 806-3531
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Academic Appointments
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{Academic Appointments}}

\noindent \textbf{Duke University}\\
\indent Assistant Professor, Department of Political Science (2023-)

\noindent \textbf{Harvard Kennedy School}\\
\indent Fellow, Shorenstein Center on Media, Politics \& Public Policy (2021-2023)

\noindent \textbf{Northeastern University}\\
\indent Senior Research Scientist, Network Science Institute (2021-2023)\\
\indent Affiliated Researcher, NULab for Text, Maps, and Networks (2022-2023) \\
\indent Part-Time Lecturer, Department of Political Science (2022-2023) \\
\indent Postdoctoral Fellow, Network Science Institute (2020-2021) \\

%\noindent Assistant Professor of Political Science, Duke University (2023-) \\
%\noindent Senior Research Scientist, Network Science Institute, Northeastern University (2021-2023)\\
%\indent Affiliated Researcher, NULab for Text, Maps, and Networks (2022-2023) \\
%\indent Part-Time Lecturer, Department of Political Science (2022-2023) \\
%\noindent Fellow, Shorenstein Center on Media, Politics \& Public Policy, Harvard Kennedy School (2021-2023)\\
%\noindent Postdoctoral Fellow, Network Science Institute, Northeastern University (2020-2021)\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{Education}}

\noindent Ph.D. in Political Science, Ohio State University, 2020 \\
\noindent B.A. with High Honors in Political Science, Kenyon College, 2014 \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{Select Publications}}
	\begin{itemize}
		\item \textbf{Green, Jon}, and Mark H. White II. 2023. \textit{Machine Learning for Experiments in the Social Sciences.} Cambridge University Press, Elements Series in Experimental Political Science.
		\item  Hobbs, William, and \textbf{Jon Green}. ``Categorizing topics versus inferring attitudes: a theory and method for analyzing open-ended survey responses." Accepted, \textit{Political Analysis}.
		\item \textbf{Green, Jon}, Stefan McCabe, Sarah Shugars, Hanyu Chwe, Luke Horgan, Shuyang Cao, and David Lazer. ``Curation Bubbles."  Accepted, \textit{American Political Science Review}.
		\item \textbf{Green, Jon}. ``The Rhetorical `What Goes with What': Political Pundits and the Discursive Superstructure of Ideology in U.S. Politics." In press, \textit{Public Opinion Quarterly}.
		\item Naftel, Daniel, \textbf{Jon Green}, Kelsey Shoub, Jared Edgerton, Mallory Wagner, and Skyler Cranmer. ``Meet the Press: Gendered Conversational Norms in Televised Political Discussions."  In press, \textit{Journal of Politics}.
		\item \textbf{Green, Jon}, Kelsey Shoub, Rachel Blum, and Lindsey Cormack. 2024. ``Cross-Platform Partisan Positioning in Congressional Speech." \textit{Political Research Quarterly} 77(3): 653–668.
		\item Robertson, Ronald E., \textbf{Jon Green}, Damian Ruck, Katherine Ognyanova, Christo Wilson, and David Lazer. 2023. ``Users choose to engage with more partisan news than they are exposed to on Google Search."\textit{Nature} 618: 342–348.
		\item \textbf{Green, Jon}, Meredith Conroy, and Ciera Hammond. 2023. ``Something to Run For: Stated Motives as Indicators of Candidate Emergence." \textit{Political Behavior} 46: 1281–1301.
		\item McCabe, Stefan, \textbf{Jon Green}, Pranav Goel, and David Lazer. 2023. ``Inequalities in Online Representation: Who follows their own member of Congress on Twitter?" \textit{Journal of Quantitative Description: Digital Media}, 3.
		\item \textbf{Green, Jon}, William Hobbs, Stefan McCabe, and David Lazer. 2022. ``Online Engagement with 2020 Election Misinformation and Turnout in the 2021 Georgia Runoff Election"  \textit{Proceedings of the National Academy of Sciences} 119(34): e2115900119.
	%	\item Joseph, Kenneth, Sarah Shugars, Ryan Gallagher, \textbf{Jon Green}, Alexi Quintana Mathé, Zijian An and David Lazer. 2021. "(Mis)alignment Between Stance Expressed in Social Media Data and Public Opinion Surveys." Proceedings of the 2021 Conference on Empirical Methods in Natural Language Processing, pages 312-324.
		\item \textbf{Green, Jon}, Jared Edgerton, Daniel Naftel, Kelsey Shoub, and Skyler Cranmer. 2020. ``Elusive Consensus: Polarization in Elite Communication on the COVID-19 Pandemic." \textit{Science Advances} 6(28): eabc2717.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{Select Awards, Grants, and Invited Talks}}
	\begin{itemize}
		\item Best Article, Information Technology \& Politics Section, American Political Science Association (w/ Stefan McCabe, Pranav Goel, and David Lazer), 2024.
		\item Generative AI in Political Science: Promise and Challenges in Research and Pedagogy. University of Florida, February 28, 2024.
		\item Presidential Primaries: Public Opinion \& Strategic Voting. The New York Chapter of the American Association for Public Opinion Research. September 20, 2023 (Remote).
		\item NetSeed Pilot Grant (w/ Sarah Shugars and Peter Levine), Network Science Institute at Northeastern University, 2021.
		\item Joint Learning Agreement with the Kettering Foundation, 2018.
	\end{itemize}

\end{document}
